Emissions and Perceptions of Climate Change

### 2022-11-17 Code/GHG_Emissions_&_Perceptions_of_Climate_Change.Rmd
Changes w/ Erika

#year <- function(x) as.POSIXlt(x)$year + 1900
# I do not know how the above code does this :(
ggplot(emissions, aes(year, emissions)) + 
  geom_path() + geom_point(aes(colour=country))+ theme_bw()

@@

```{r}
belief_glm<-glm(Number~response, data=beliefs, family= Gamma(link='inverse') ) #Constructing the general linear model
#The family (or ‘error’) part of a GLM is not too difficult to understand. This bit just determines what kind of distribution is used to describe the response variable. A general linear model always assumes normality— that’s pretty much its defining feature in fact—but with a generalized linear

@@

@@

```{r}
ggplot(worry, aes(response,Number, fill=Country))+geom_bar(stat = 'identity', position = 'dodge') + xlab("Response to Survey Question")+ ylab("Percent") + theme_bw() + coord_flip()
```
32% of Americans are very worried about climate change, wherease oonly 21% of Danes are. But 52% of Danes are somewhat worried at only 36% are. To better visualize this lets try another graph.

>>>>

#year <- function(x) as.POSIXlt(x)$year + 1900
# I do not know how the above code does this :(
ggplot(emissions, aes(year, emissions, colour= country, group=country)) +  geom_line() +
  geom_point(aes(colour=country))+ theme_bw()

@@

```{r}
beliefs<- beliefs %>% mutate(frequency=Number/100)
belief_glm<-glm(frequency~response, data=beliefs, family= binomial) #Constructing the general linear model
#The family (or ‘error’) part of a GLM is not too difficult to understand. This bit just determines what kind of distribution is used to describe the response variable. A general linear model always assumes normality— that’s pretty much its defining feature in fact—but with a generalized linear

@@

```

```{r}
ggplot(beliefs, aes(frequency, group=Country, fill=Country, position='dodge'))+ geom_histogram()+theme_bw()
```

Test autoplot

@@

```{r}
ggplot(worry, aes(response,Number, fill=Country))+geom_bar(stat = 'identity') + xlab("Response to Survey Question")+ ylab("Percent") + theme_bw() + coord_flip()
```
32% of Americans are very worried about climate change, wherease oonly 21% of Danes are. But 52% of Danes are somewhat worried at only 36% are. To better visualize this lets try another graph.
